---
title: "Digitization tool"
author: "Jasper Zhang"
date: "2023-06-05"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r ,echo=FALSE, warning=FALSE, message= FALSE}
# install required packages using pacman package
#install.packages("pacman")
```


```{r ,echo=FALSE, warning=FALSE, message= FALSE}
# Install and load packages
# Load pacman
library(pacman)
p_load(here, ggplot2, jpeg, dplyr, tidyr, stringr, imager, magick,readxl, kableExtra, SurvdigitizeR)
rm(list = ls())
```


# Guide for Digitizing KM Curves

This guide will walk you through the process of digitizing Kaplan-Meier (KM) curves  , We will first discuss the input to the digitization process, followed by a complete digitization example for the  KMcurve.png. The digitized results will be saved in both CSV and image formats.


# Example of Digitizing  KMcurve.png

## Digitization input


* img_name set to  "KMcurve.png", t_img_path is set to curve in "vignettes" folder.

* number of curves: 2

* x range: 0 - 10 by 1

* y range: 0 - 1 by 0.25

* y_text_vertical: TRUE, set to TRUE if the number on y axis is in vertical direction.

* impute_size: 0, the number of time intervals for curve overlapping check, 0 for skipping the step, suggested values: 20, 40, etc.

```{r}
img_name          = "KMcurve.png"
t_img_path        =  paste0(here::here("vignettes"),"/",img_name)

t_num_curves      = 2     # there are two curves in the plot

t_x_start         = 0     # x axis range: 0 to 33 by step size 3
t_x_end           = 10
t_x_increment     = 1

t_y_start         = 0     # y axis range: 0 to 1 by step size 0.1
t_y_end           = 1
t_y_increment     = 0.25
t_y_text_vertical = TRUE  # the direction of number text on y axis, TRUE means vertical,
                          #the same direction as text on x axis

t_impute_size     = 0    # the number of time intervals for curve overlapping check,
                          # higher number shorter intervals.
                          # 20,40 are suggested values
```


## Digitization Step


```{r , warning=FALSE, message= FALSE}
out <- survival_digitize(img_path = t_img_path,
                          num_curves = t_num_curves ,
                          x_start = t_x_start,  x_end = t_x_end,  x_increment = t_x_increment,
                          y_start = t_y_start,  y_end = t_y_end,  y_increment = t_y_increment,
                          y_text_vertical = t_y_text_vertical,
                          impute_size = 0)

```

## Save the Result to a CSV file

* numerical result will be saved to "vignettes/digitized_data" folder.


```{r}
write.csv(out,here::here("vignettes","digitized_data",
                         paste0("out_put_", img_name,"_Auto_Digitized.csv")),
          row.names = FALSE)
```


## Plot the Digitization

* specify plot details (x-range, y-range) for displaying digitization result in the same format as input


```{r}
result_name   = img_name

out %>% 
  ggplot(aes(x = time, y= St, color = as.factor(curve), group = curve)) +
  geom_step() + theme_bw() + labs(color='Curves') + 
  scale_color_manual(values = c("1" = "red", "2" = "blue")) +
  scale_x_continuous(limits = c(t_x_start, t_x_end),
                     breaks = seq(t_x_start, t_x_end, by = t_x_increment))+
  scale_y_continuous(limits = c(t_y_start, t_y_end),
                     breaks = seq(t_y_start, t_y_end, by = t_y_increment))+
  ggtitle(paste0(result_name,"_Digitized"))

```

## Save the Plot

* The result will be saved in "vignettes/digitized_plot/" folder.


```{r}
  axis_info<- axes_identify(fig.hsl = img_read(path = t_img_path))
  fig.cropped <- axis_info$fig.hsl
  save_height = 5
  save_width = save_height * dim(fig.cropped)[2]/dim(fig.cropped)[1]
  img_save_name = paste0(here::here("vignettes","digitized_plot/"),
                         result_name,"_Auto_Digitized.png")
  ggsave(img_save_name,width = save_width , height = save_height,)
```



